%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% This is a modified ONE COLUMN version of
% the following template:
% 
% Deedy - One Page Two Column Resume
% LaTeX Template
% Version 1.1 (30/4/2014)
%
% Original author:
% Debarghya Das (http://debarghyadas.com)
%
% Original repository:
% https://github.com/deedydas/Deedy-Resume
%
% IMPORTANT: THIS TEMPLATE NEEDS TO BE COMPILED WITH XeLaTeX
%
% This template uses several fonts not included with Windows/Linux by
% default. If you get compilation errors saying a font is missing, find the line
% on which the font is used and either change it to a font included with your
% operating system or comment the line out to use the default font.
% 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% 
% TODO:
% 1. Integrate biber/bibtex for article citation under publications.
% 2. Figure out a smoother way for the document to flow onto the next page.
% 3. Add styling information for a "Projects/Hacks" section.
% 4. Add location/address information
% 5. Merge OpenFont and MacFonts as a single sty with options.
% 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% CHANGELOG:
% v1.1:
% 1. Fixed several compilation bugs with \renewcommand
% 2. Got Open-source fonts (Windows/Linux support)
% 3. Added Last Updated
% 4. Move Title styling into .sty
% 5. Commented .sty file.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% Known Issues:
% 1. Overflows onto second page if any column's contents are more than the
% vertical limit
% 2. Hacky space on the first bullet point on the second column.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\documentclass[]{deedy-resume-openfont}


\begin{document}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     LAST UPDATED DATE
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\lastupdated

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     TITLE NAME
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%


\namesection{Yumin}{Xia}{ \urlstyle{same}\url{https://irl.cs.ucla.edu/~yumin/} \\
\href{mailto:yuminx@ucla.edu}{yuminx@ucla.edu} | 310-694-1760
}

%% \href{http://linkedin.com/in/12346}{http://linkedin.com/in/12346}

%% \begin{center}
%% \huge\color{subheadings}\custombold{LIFELONG LEARNER}
%% \end{center}


\section{Education}
\runsubsection{University of California, Los Angeles}
\descript{| Master in Computer Science}
\location{Sept. 2016 - Dec. 2017 | LA U.S. \textbullet{} GPA: 3.97 / 4.00}
 
\runsubsection{Xi’an Jiaotong University}
\descript{| B.Eng in Computer Science and Technology}
\location{Sept. 2012 - Jun. 2016 | Xi'an, China \textbullet{} Major GPA: 88 / 100}

\section{Industrial Experience}

\runsubsection{Barefoot Networks, Compiler Team}
\descript{| Software Engineering}
\location{Nov. 2017 – Present | Santa Clara, California, USA}
\begin{tightemize}
\item We are building a compiler for the fastest programmable switch on earth! Currently, I am working on design and implementation of Packet Header Vertor allocation algorithm. Parser related register allocation and optimizations.
\end{tightemize}
\sectionsep

\runsubsection{Google, Display \& Video Ads Team}
\descript{| Software Engineering Intern}
\location{Jun. 2017 – Sept. 2017 | MTV, California, USA}
\begin{tightemize}
\item A screen-diff test tool: when a rendering-server-related code change is submitted for code review, this tool will be triggered automatically, to build and run two different version of rendering server, replay traffic, render the returned result HTML content into images, and compare the rendered image. Unexpected differences will be captured and screen-diff image, alone with html differences, will be reported to the submitter.
\item A protobuf search tool: For a given query (SQL-like syntax on protobuf fields), returns a set of matched protobufs. This tool extracts ~2.4M protobufs out from ~60GB binary logs hourly, indexes specified fields, and save them to Bigtable. It can return a result set in less than one second, out from ~60M protobufs. The query syntx support exact or fuzzy match, on all types of protobuf fields (e.g. int, string, enum, and nested fields..), and it supports the 'has-a' query on 'repeated fields' (array), which can be combined with both fuzzy/exact match.
\end{tightemize}
\sectionsep


\runsubsection{Chongqing PERK Culture Communication Co., Ltd}
\descript{| Co-founder, CTO \break Full stack web developer}
\location{Jan. 2013 – Aug. 2016 | Chongqing, China}
Designed and developed a web application (called ‘.Flip’) to support PerkSummit®, one of the most influential student conferences in southwestern China.
This system includes student application management system, class enrollment, payment interface, a game-like badge system, and an internal social network.
It is used by thousands of students and the admission committee of PerkSummit®.
Server-side: PHP, CodeIgniter. Client-side: Bootstrap, jQuery; Database: MySQL.
\sectionsep



\section{Academic Experience}

\runsubsection{Research in Named-Data Networking (NDN)}
\descript{\break System software development in modern C++}
\location{Aug. 2015 – Otc. 2017 | Internet Research Lab, UCLA}

\begin{tightemize}
\item Domain Name Service for Named Data Networking (NDNS). Design and implementation of: the NDNS security schema, NEC-like denial of existence, cache resolver, validator, and a certificate fetcher for NDNS. Publication at ICCCN: \href{https://named-data.net/publications/2017-icccn-ndns/}{NDNS}. Source code: \href{https://gerrit.named-data.net/#/q/project:ndns}{gerrit}
\item Implementation and evaluation of several NDN cache policies based on NDNsim: \href{https://github.com/ndncomm/nfd-caching-policies}{github repo}.
%% \item Design and implementation of a hop-by-hop congestion control algorithm in NDN.
%% \item Software development in Named-data Networking Forwarding Daemon (NFD)
\end{tightemize}
\sectionsep


\runsubsection{The ACM/ICPC International Collegiate Programming Contest}
\descript{\break Captain of team ‘StRcPy’, assistant coach of XJTU}
\location{Sept. 2012 – Sept. 2015 | Xi'an, China}
\begin{tightemize}
\item Silver Medal of The ACM-ICPC Asia Regional Guangzhou Site 2014
\item Gold Medal and Fifth Place of The ACM-ICPC Multi-Provincial Programming Contest Chengdu Site 2013
\item Gold Medal and First Place of The ACM-ICPC Shaanxi Provincial Programming Contest 2013
\item Web-Based ACM Training System of XJTU, abilities includes remote code submitting and judging, code management among ACM competitors in XJTU, and training plan management.
\end{tightemize}
\sectionsep

\runsubsection{Selected Projects}
\descript{\break Software formal verification and visualization, IoT, Hardware...}
\begin{tightemize}
\item \href{https://github.com/Stumble/TrustCoq}{TrustCoq}: Using machine-checked formal verification technique(Coq) to proof termination on a domain-specific language. The language describes the security schema of NDN applications. Specifically, this project formally proofef that, as long as a polcy, described in this language, can pass the termination check, it will terminate in a finite number of steps.
\item \href{https://github.com/Stumble/duck}{DUCK}: a dynamic universal software system visualization kit. This tool execute syntactical analysis on source code to produce interactive query-able figures to help programmer understand the software structure. The query-able interative feature addresses the scalability issue of visulization by letting user specify the what they want. Currently, C++ are supportted, based on libclang.
\item \href{https://github.com/Stumble/smartGG}{Smart Gas Guardian}: a smart home device prototype that could automatically adjust house’s moisture and temperature, detect hazardous gases using MQ series sensor, and send alert message to user’s phone if an emergency happens, using Raspberry Pi as gateway, connected to devices via Bluetooth.
\item A pipelined CPU implementation on FPGA chips with the MIPS32 instruction set, using High-Level Synthesis Technique.
\end{tightemize}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     RESEARCH
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%


\section{Programming Skills}
\begin{minipage}[t]{.6\textwidth}
\subsection{Languages}
\location{Over 5000 lines and used in production}
C/C++ \textbullet{} Python \textbullet{} PHP \textbullet{} JavaScript \\
\location{Over 2000 lines:}
Coq(Gallina) \textbullet{} Assembly \textbullet{} \\
\location{Familiar:}
Java

\sectionsep
\end{minipage}
\hfill
\begin{minipage}[t]{.35\textwidth}
\subsection{Other Skills}
\location{Operating System:}
Debian/Ubuntu\\
\location{Version Control:}
git \textbullet{} gerrit\\
\end{minipage}

%% NDNS bib
%% @article{afanasyevndns,
%%   title={NDNS: A DNS-Like Name Service for NDN},
%%   author={Afanasyev, Alexander and Jiang, Xiaoke and Yu, Yingdi and Tan, Jiewen and Xia, Yumin and Mankin, Allison and Zhang, Lixia}
%% }

\end{document}  \documentclass[]{article}